---
title: "StatsResource"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


```{r child = 'main/introduction.Rmd'}
```




Discrete Random Variable
======================================

*  Examples of discrete random variables include the number of children in a family, the Friday night attendance at a cinema, the number of patients in a doctor's surgery, the number of defective light bulbs in a box of ten.

*  For a discrete random variable observed values can occur only at isolated points along a scale of values. In other words, observed values must be integers.
*  Consider a six sided die: the only possible observed values are 1, 2, 3, 4, 5 and 6. 
*  It is not possible to observe values that are real numbers, such as 2.091.

*  *(Remark: it is possible for the average of a discrete random variable to be a real number.)*

*  For a discrete random variable observed values can occur only at isolated points along a scale of values. 
*  For a six sided dice, the only possible observed values are 1, 2, 3, 4, 5 and 6. It is not possible to observe values such as 5.732.

*  For a continuous random variable all possible fractional values of the variable cannot be listed, and
therefore the probabilities that are determined by a mathematical function are portrayed graphically by a
probability density function, or probability curve.



### Expected Value for Discrete Random Variables

The expected value of a random variable X is symbolised by E(X) or $mu$.


If X is a discrete random variable with possible values $\{ x1, x2, x3,\ldots , xn\}$, and$ p(x_i)$ denotes P(X = xi), then the expected value of X is defined by: 

\[E(X) = \sum x_i \times P(x_i) \]

where the elements are summed over all values of the random variable X. 


### Discrete Random Variables

A random variable is a numerical description of the outcome of an experiment.

Random variables can be classified as discrete or continuous, depending on the numerical values they may take.

A ranom variable that may assume any numerical value in an interval or collection of intervals is called a continuous random variable.

### Worked Examples 

Suppose a fair coin is tossed six times. The number of heads which can occur with their respective
probabilities are as follows:

xi0123456
p(xi)1/646/6415/6420/6415/646/641/64

a)Compute the expected value (i.e. expected number of heads).
b)Compute the variance of the number of heads.




### Tutorial Sheet

<h3> Tutorial Sheet </h3>

<h5> Worked Example 1 </h5>

The probability distribute of discrete random variable $X$ is tabulated below. 
There are 5 possible outcome of $X$, i.e. 1, 2, 4, 6 and 8.
\begin{center}
\begin{tabular}{|c||c|c|c|c|c|}
\hline
$x_i$  & 1 & 2 & 4 & 6 & 8  \\\hline
$p(x_i)$ & 0.50 & 0.15 & 0.20 & 0.05 & 0.10 \\
\hline
\end{tabular}
\end{center}

a. Compute the value of $k$.
b. What is the expected value of X?
c. Compute the value of $E(X^2)$.
d. Given that $E(X^2) = 12.5$, compute the variance of $X$.



---------------------------------------------------------------------------

<h5> Worked Example 2 </h5>

The probability distribution of discrete random variable $X$ is tabulated below. 
There are 5 possible outcomes of $X$, i.e. 1, 2, 3, 5 ,10 and 20.
\begin{center}
\begin{tabular}{|c||c|c|c|c|c|}
\hline
$x_i$  & 1 & 2 & 5 & 10 & 20 \\\hline
$P(x_i)$ &  0.10 & 0.25 & 0.30& 0.20 &0.15\\

\hline
\end{tabular}
\end{center}

a. Determine the expected value $E(X)$.
b. Evaluate $E(X^2)$.
c. Compute the variance of random variable $X$.


