---
title: "StatsResource"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```



Statistics {data-navmenu="Introductory Statistics"}
=====================================

Column 
--------------------

Measures of Centrality {data-navmenu="Introductory Statistics"}
==============================================================

Column
-------------------------------------------------------------

```{r child = 'probability/Probability.Rmd'}
```

```{r child = 'probability/RandomVariables.Rmd'}
```

Joint Random Variables {data-navmenu="Probability"}
====================================
Column
-------------------------------

### Joint Probability Distributions

```{r child = 'probability/DiscreteDistributions.Rmd'}
```

```{r child = 'probability/PoissonDistribution.Rmd'}
```

```{r child = 'probability/NormalDistribution.Rmd'}
```

```{r child = 'probability/ContinuousDistributions.Rmd'}
```

```{r child = 'probability/ApproximatingDistributions.Rmd'}
```

```{r child = 'probability/CompoundDistributions.Rmd'}
```




 	  	
```{r child = 'randomvariables/MomentGeneratingFunctions.Rmd'}
```




```{r child = 'inference/SamplingDistributions.Rmd'}
```

```{r child = 'inference/Proportions.Rmd'}
```

```{r child = 'inference/NonParametricTests.Rmd'}
```



Linear Models {data-navmenu="Modelling Data"}
==================================

Column {.tabset}
-----------------------------

### Correlation


* <a href= https://www.youtube.com/watch?v=3Y3pJaLcXdc">Correlation Coefficient - Hypothesis Testing </a>


### Multiple regression


<li>Variable Selection Procedures: Use of Forwards and Backwards elimination in multiple regression.</li>
	<li>Use of F tests.</li>
	<li>The Akaike Information Criterion</li>
	<li>Polynomial regression. (<em>Simple cases only.</em>)</li>
	<li>Use of indicator variables to model factors or qualitative variables (<em>Simple cases only.</em>)</li>

```{r child = 'modellingdata/BivariateData.Rmd'}
```


```{r child = 'modellingdata/ModelSelection.Rmd'}
```

```{r child = 'modellingdata/ResidualAnalysis.Rmd'}
```

```{r child = 'modellingdata/RegressionANOVA.Rmd'}
```

```{r child = 'modellingdata/SurvivalAnalysis.Rmd'}
```

```{r child = 'specialtopics/GameTheory.Rmd'}
```

```{r child = 'specialtopics/RandomNumberGeneration.Rmd'}
```

```{r child = 'specialtopics/StatisticalProcessControl.Rmd'}
```

```{r child = 'specialtopics/ExperimentalDesign.Rmd'}
```

```{r child = 'specialtopics/DecisionTheory.Rmd'}
```

```{r child = 'specialtopics/NetworkAnalysis.Rmd'}
```

#### Unsorted

<ul>
<li>	<a href="https://youtu.be/Qs4lOegQNbA/">	One-Way ANOVA - Calculating the Least Significant Difference	</a>	</li>
<li>	<a href="https://youtu.be/g666XEXVpL0/">	Rules of Probability - Mutually Exclusive and Independent Events	</a>	</li>
				
				
<li>	<a href="https://youtu.be/5F0jSp1bOEU/">	Computing Sample Variance	</a>	</li>
				
				
				
				
				
<li>	<a href="https://youtu.be/24PPecNK7NI/">	Mixed Probability Distributions	</a>	</li>
<li>	<a href="https://youtu.be/jdpHIFyX-6g/">	The Sign Test : Hearing Test Example (Non Parametric Hypothesis Testing)	</a>	</li>
<li>	<a href="https://youtu.be/_Ob48DhL4Yo/">	Normal Random Variables - Bicycle Journey Example	</a>	</li>
				
				
<li>	<a href="https://youtu.be/4fOcxafPHow/">	Survival Analysis - Kaplan Meier Estimates of the Survival Function	</a>	</li>
<li>	<a href="https://youtu.be/HJ4DR79XRa8/">	Computing the Z score	</a>	</li>
<li>	<a href="https://youtu.be/droO8NykzY8/">	Expected Value of Sample Variance	</a>	</li>
<li>	<a href="https://youtu.be/pIAZmkRvKPo/">	Geometric Distribution with Chi Square Test for Goodness of Fit	</a>	</li>
<li>	<a href="https://youtu.be/ay-Y_SUslP8/">	Hypergeometric Distribution - Worked Example	</a>	</li>
<li>	<a href="https://studio.youtube.com/channel/UCU8y8xt6IcvARijbLzx2txw/videos/upload?filter=%5B%5D&sort=%7B%22columnType%22%3A%22date%22%2C%22sortOrder%22%3A%22DESCENDING%22%7D"	Joint Density Functions for Discrete Random Variables	</a>	</li>
				
				
<li>	<a href="https://youtu.be/URzJiQP9E3c/">	Linear Regression   Part B	</a>	</li>
<li>	<a href="https://youtu.be/093X1SWd1cg/">	Uniform Random Variables	</a>	</li>
<li>	<a href="https://youtu.be/5DY3j8nw5sg/">	Working With Small Samples	</a>	</li>
</ul>
