---
title: "StatsResource"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```



Statistics {data-navmenu="Introductory Statistics"}
=====================================

Column 
--------------------

Measures of Centrality {data-navmenu="Introductory Statistics"}
==============================================================

Column
-------------------------------------------------------------



```{r child = 'probability/RandomVariables.Rmd'}
```

Joint Random Variables {data-navmenu="Probability"}
====================================
Column
-------------------------------

### Joint Probability Distributions

```{r child = 'probability/DiscreteDistributions.Rmd'}
```

```{r child = 'probability/PoissonDistribution.Rmd'}
```

```{r child = 'probability/NormalDistribution.Rmd'}
```

```{r child = 'probability/ContinuousDistributions.Rmd'}
```

```{r child = 'probability/ApproximatingDistributions.Rmd'}
```

```{r child = 'probability/CompoundDistributions.Rmd'}
```




 	  	
```{r child = 'randomvariables/MomentGeneratingFunctions.Rmd'}
```




```{r child = 'inference/SamplingDistributions.Rmd'}
```

```{r child = 'inference/Proportions.Rmd'}
```

```{r child = 'inference/NonParametricTests.Rmd'}
```



Linear Models {data-navmenu="Modelling Data"}
==================================

Column {.tabset}
-----------------------------

### Correlation


* <a href= https://www.youtube.com/watch?v=3Y3pJaLcXdc">Correlation Coefficient - Hypothesis Testing </a>


### Multiple regression


<li>Variable Selection Procedures: Use of Forwards and Backwards elimination in multiple regression.</li>
	<li>Use of F tests.</li>
	<li>The Akaike Information Criterion</li>
	<li>Polynomial regression. (<em>Simple cases only.</em>)</li>
	<li>Use of indicator variables to model factors or qualitative variables (<em>Simple cases only.</em>)</li>

```{r child = 'modellingdata/BivariateData.Rmd'}
```


```{r child = 'modellingdata/ModelSelection.Rmd'}
```

```{r child = 'modellingdata/ResidualAnalysis.Rmd'}
```

```{r child = 'modellingdata/RegressionANOVA.Rmd'}
```

```{r child = 'modellingdata/SurvivalAnalysis.Rmd'}
```

```{r child = 'specialtopics/GameTheory.Rmd'}
```

```{r child = 'specialtopics/RandomNumberGeneration.Rmd'}
```

```{r child = 'specialtopics/StatisticalProcessControl.Rmd'}
```

```{r child = 'specialtopics/ExperimentalDesign.Rmd'}
```

```{r child = 'specialtopics/DecisionTheory.Rmd'}
```

```{r child = 'specialtopics/NetworkAnalysis.Rmd'}
```