---
title: "StatsResource"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


```{r child = 'main/introduction.Rmd'}
```

```{r child = 'dataanalysis/descriptivestatistics.Rmd'}
```

```{r child = 'dataanalysis/exploratorydataanalysis.Rmd'}
```




```{r child = 'main/quantiletables.Rmd'}
```
```{r child = 'main/probabilityformulas.Rmd'}
```

```{r child = 'main/regressionformulas.Rmd'}
```







```{r child = 'specialtopics/RandomNumberGeneration.Rmd'}
```

```{r child = 'specialtopics/StatisticalProcessControl.Rmd'}
```



Unsorted {data-navmenu="Special Topics"}
==============================================================

Column
--------------------------------

* <a href="https://youtu.be/Qs4lOegQNbA/">	One-Way ANOVA - Calculating the Least Significant Difference	</a>	
* <a href="https://youtu.be/g666XEXVpL0/">	Rules of Probability - Mutually Exclusive and Independent Events	</a>	
				
				
	
				
				
				
				
				
* <a href="https://youtu.be/24PPecNK7NI/">	Mixed Probability Distributions	</a>	
* <a href="https://youtu.be/jdpHIFyX-6g/">	The Sign Test : Hearing Test Example (Non Parametric Hypothesis Testing)	</a>	
* <a href="https://youtu.be/_Ob48DhL4Yo/">	Normal Random Variables - Bicycle Journey Example	</a>	
				
				
* <a href="https://youtu.be/4fOcxafPHow/">	Survival Analysis - Kaplan Meier Estimates of the Survival Function	</a>	
* <a href="https://youtu.be/HJ4DR79XRa8/">	Computing the Z score	</a>	
* <a href="https://youtu.be/droO8NykzY8/">	Expected Value of Sample Variance	</a>	

* <a href="https://youtu.be/URzJiQP9E3c/">	Linear Regression   Part B	</a>	
* <a href="https://youtu.be/093X1SWd1cg/">	Uniform Random Variables	</a>	

