---
title: "Information Theory"
output: 
  flexdashboard::flex_dashboard:
    theme: united
    css: style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
Information Theory
==================

### Introduction to Information Theory
Information theory is a process that focuses on the task of quantifying information. 
The quantification of information is achieved by identifying viable methods of compressing and communicating data without causing 
and degradation in the integrity of the data. Information theory can be utilized in a number of different fields, including quantum computing, 
data analysis and cryptography.
<p>

#### Clause Shannon

The origin of modern informational theory is usually attributed to Claude E. Shannon. His work A Mathematical Theory of Communication, first published in 1948, 
lays the foundation for the quantification and compression of data into viable units that may be stored for easy retrieval later. 
His basic approach provided the tools necessary to enhance the efficiency of early mainframe computer systems, and translated easily into 
the advent of desktop computers during the decade of the 1970’s.

<p>

As a branch of both electrical engineering and applied mathematics, information theory seeks to uncover the most efficient 
methods of conveying data, within the limits inherent in the data proper. The idea is to ensure that the mass transit of data does 
not in any way decrease the quality, even if the data is compressed in some manner. 

Ideally, the data can be restored to its original form upon reaching its destination. 
In some cases, however, the goal is to allow data in one form to be converted for mass transmission, 
received at the point of termination, and easily converted into a format other than the original without losing any of the transmitted information.


```{r child = 'entropy.Rmd'}
```


```{r child = 'codeclassification.Rmd'}
```


Data compression
=================================
<h4> Data Compression</h4>
Data compression is the science (and art) of representing information in a compact form. Having been the domain of a relatively small group of engineers and scientists, it is now ubiquitous.
<p>
It has been one of the critical enabling technologies for the on-going digital multimedia revolution for decades. Without compression techniques, none of the ever-growing Internet, digital TV, mobile communication or increasing video communication would have been practical developments. <p>

<p>

Data compression is an active research area in computer science. By "compressing data", we actually mean deriving techniques or, more specifically, designing efficient algorithms to:


1. represent data in a less redundant fashion
2. remove the redundancy in data
3. implement coding, including both encoding and decoding.
<p>



```{r child = 'informationcontent.Rmd'}
```

```{r child = 'informationrate.Rmd'}
```

```{r child = 'kraftinequality.rmd'}
```

